### 2014-09-06 abstract.tex
abs

\begin{abstract}
Predictive analysis has recently emerged as a promising paradigm for sound detection of multithreading bugs (i.e., without false alarms). Intuitively, the idea is to start from an instrumented execution trace, and transform it based on the concrete information it provides (e.g., concrete values and memory accesses) while preserving feasibility (e.g., by reodering trace events iff flow dependencies are preserved).

@@

In this paper, we present \sysname, a predictive race detector that is able to relax both of these restrictions while guaranteeing soundness, as we prove formally. Thanks to its ability to explore event orderings that violate flow dependencies as well as unexecuted branches, \sysname\ is able to detect x$2.5$ more data races on a representative set of large-scale benchmarks compared to the state-of-the-art in predictive race detection.
\end{abstract}

>>>>

\begin{abstract}
Predictive analysis has recently emerged as a promising paradigm for sound detection of multithreading bugs (i.e., without false alarms). The idea is to start from an instrumented execution trace, and transform it based on the concrete information it provides (e.g., concrete values and memory accesses) while preserving feasibility (e.g., by reodering trace events iff flow dependencies are preserved), such that bugs are exposed.

@@

In this paper, we present \sysname, a predictive race detector that is able to relax both of these restrictions while guaranteeing soundness, as we prove formally. Thanks to its ability to explore event orderings that violate flow dependencies as well as unexecuted branches, \sysname\ is able to detect x$2.5$ more data races on a representative set of large-scale benchmarks compared to the state of the art in predictive race detection.
\end{abstract}
